---
title: "Lab: The 12 Days of Christmas"
author: "Group 4"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages for Functions
library(dplyr)
library(glue)
library(stringr)
library(purrr)
```


### A Test Dataset

Run the code below to load up a dataset called `xmas` that contains the crucial 
information about the gifts in the song. We will use this dataset to test out
our functions as we work on them.

```{r}
xmas <- read.csv("https://www.dropbox.com/s/e584pryn8evm1gz/xmas.csv?dl=1")
xmas_small <- filter(xmas, Day == 1 | Day == 2 )
```

---

## Step One:  Plurals

Note that the gifts are listed in singular: for example, on day five the
narrator receives "five golden rings", but the entry in the dataset for the gift
on day 5 simply says "ring".  

Using the skeleton of the `pluralize_gift()` function, complete the code so that 
the function takes a gift and returns the appropriate plural. 

```{r}
# Function that takes a noun and makes it plural
# Arguments -- gift -- A string or vector of strings
# Return -- A string or vector of strings with the pluralized words

pluralize_gift <- function(gift){
  
  if(gift[-1] == "y") {
    gift <- gift %>%
    str_replace("y$", "ies")
  }
else {
  gift <- gift %>%
  str_replace("$", "s")
  str_replace("oo", "ee")
}
  
return(gift)

}
```

```{r}
pluralize_gift <- function(gift){

  ifelse(gift[-1] != "y",
          gift <- gift %>%
          str_replace("$", "s"),
          gift <- gift %>%
          str_replace("y$", "ies")
          )
  gift <- gift %>%
    str_replace("oo", "ee")
  
return(gift)

}
```

```{r non vectorized}
pluralize_gift <- function(gift){

  if(str_detect(gift, "oo")){
    return(str_replace(gift, "oo", "ee"))
  }
  if_else(gift[-1]  == "y",
          gift <- gift %>%
    str_replace("y$", "ie"),
      gift <- gift %>%
    str_replace("$", "s"))
return(gift)
}
```


```{r}
pluralize_gift("lady")

```

*Hint 1:* Note that the gifts on days six and nine have unusual pluralizations.
You may assume that in other datasets, there will be no special cases besides
these types.

*Hint 2:*  The following small example may be useful to you:

```{r, eval = TRUE}
my_names <- c("Kimberly", "Trini", "Jason", "Billy", "Zach", "Tommy")

my_names %>% 
  str_replace("y$", "ies")
```


**Important:**  You should **absolutely not** "hard-code" anything into this 
function; this function should work in general, not just for the items in the
12 Days of Christmas.  For example, the word "rings" should not appear anywhere
in the function.  I should be able to give it any gift and any day, and get back
the plural of that gift.


### Test Your Function

Try your function out on the gifts in the dataset.  
(Consider: is your function *vectorized*?  It does not have to be, but it may
make things simpler!)

```{r}

pluralize_gift(xmas$Gift.Item)

purrr::map_chr(xmas$Gift.Item, pluralize_gift)

```


---


## Step Two: Creating sentences

Write a function called `make_phrase` that takes as input the necessary information, 
and returns a phrase.  For example, 

```{r}
make_phrase(num = 1, 
            num_word = "one", 
            item = "lord", 
            verb = "a-leaping", 
            adjective = "", 
            location = "")
```

should return

```
"ten lords a-leaping"
```

```{r}
make_phrase <- function(num, num_word, item, verb, adjective, location) {
  
  ## Step 1: Replace NAs with blank strings
  num <- str_replace_na(num, "")
  verb <- str_replace_na(verb, "")
  num_word <- str_replace_na(num_word, "")
  item <- str_replace_na(item, "")
  adjective <- str_replace_na(adjective, "")
  location <- str_replace_na(location, "")
  ## Step 2: Pluralize the gift if needed
  ## Items with numbers larger than 1 should be pluralized
  ## Single items starting with a vowel should have "an" in front
  ## All other single items should have "a" in front
  
  vowel_start <- str_sub(item, 1, 1) %>% str_detect("^[aeiou]")
  
  if (num > 1) {
    
    item <- pluralize_gift(item)
    
  } else if (vowel_start) {
  
    item <- str_c("an", item, sep = " ")
    
  } else {
    
    item <- str_c("a", item, sep = " ")
    
  }
  
  glue::glue("{num_word} {adjective} {item} {verb} {location}") %>%
    str_squish()
  
  
}
```


# Test Your Function

Try your function out on the `xmas` data, by making a new variable containing
the daily phrases.

**Hint:** The `Day.in.Words` variable isn't quite what you want! You want `12`
to say `"twelve"` **not** `"twelfth"`. I suggest using the **english** package
to create numbered days and then use those in your `pmap_chr()`!

```{r}
xmas <- xmas %>%
  mutate(
    Day.in.Words = as.character(english::as.english(Day)),
    Full.Phrase = pmap_chr(list(Day, Day.in.Words, Gift.Item, Verb, Adjective, Location), 
                           make_phrase)
  )
```


---


## Step Three:  Iteration.

Write a function called `sing_line` that takes as input:

* A dataset

* A number indicating which day to sing about

* The name of a column in the dataset that contains the phrases for each day.

```{r mine}
# Produces the string for one day of the song.
# Arguments -- dataset -- A data frame containing information about gifts
# Arguments -- line -- The number of the line for the day you want to sing about
# Arguments -- phrase_col -- The variable name for the column in the dataset that contains the gift phrases
# Return -- A string singing the line of the song with all gifts for the given day.

sing_line <- function(dataset, line, phrase_col){
  
  # Step 1: Setup the intro line
  
  num_word <- english::ordinal(line)
  
  intro <- glue::glue("On the {num_word} day of Christmas, my true love sent to me, \n")
  
  # Step 2: Sing the gift phrases

    phrases <- dataset %>% 
      filter(Day <= line) %>%
      pull({{phrase_col}}) %>%
      rev()
    
    #sing_phrases <- vector(mode = "character");
    
    #for (i in seq(from = line + 1, to = 1)) {
     # sing_phrases <- str_c(phrases[i])
    #}
#english::ordinal()
  ## put it together
    
  final_phrases <- paste(phrases, collapse =" \n ")
    glue::glue("{intro} {final_phrases}")
  final_line <- str_c(intro, final_phrases)
  return(final_phrases)
  }

#for i in sequence()


```

For example,


```{r}
sing_line(dataset = xmas, 
          line = 2, 
          phrase_col = Full.Phrase)

```

```{r abdul}
sing_line <- function(dataset, line, phrase_col){

  # Step 1: Setup the intro line

  num_word <- english::ordinal(line)
 
  intro <- glue::glue("On the {num_word} day of Christmas, my true love sent to me,")
  # Step 2: Sing the gift phrases

    phrases <- dataset %>%
      filter(Day <= line) %>% 
      pull({{phrase_col}}) %>% 
      rev()
    #print(phrases[line])
    if (str_detect(phrases[line], "one"))
    {
      phrases[line] <- str_replace(phrases[line], "one", "a")
    }
    a<- #map_chr(1:line, glue::glue("{phrases},\n"))
      paste(phrases[1:(line-1)], collapse = ",\n")
    b <- str_c(a, phrases[line], sep = "\nand ")
    return (glue("{intro}\n{b}"))

}
```

We learned about the paste function from <https://www.journaldev.com/40396/paste-in-r>
should return

```
On the second day of Christmas, my true love sent to me,
two turtle doves 
and a partridge in a pear tree.
```

*Hint:*  The `{{phrase_col}}` part, which I provided for you, lets you use 
column names as arguments to a function.  Don't delete that line of code!

---

## Step Four: Use Your Functions!

Run the following code to test out your functions! The ouput should be the 
lyrics for the entire 12 Days of Christmas song. 

```{r}
xmas2 <- xmas %>%
  mutate(
    day.num = as.character(english::english(Day)), 
    Full.Phrase = pmap_chr(list(num = Day, 
                                num_word = day.num, 
                                item = Gift.Item, 
                                verb = Verb, 
                                adjective = Adjective, 
                                location = Location), 
                           make_phrase)
  )

map_chr(1:12, ~sing_line(xmas2, .x, Full.Phrase)) %>%
  str_c(collapse = "\n") %>%
  cat()

```


## Step Five: Show Me Your Work! 

#### Get it on GitHub

Once you are done with all the functions, make sure you have **pushed** your
work to GitHub.

Make sure your repository contains your completed RMarkdown document and
knitted HTML. 

- Your HTML should **only** show the code for your functions and output from 
testing / verifying that your functions perform as they should. 

__If you used GitHub to store your work:__

Submit the link to your GitHub repository in the Lab 8 assignment portal. 

__If you downloaded the compressed folder and did not use GitHub:__

Submit **both** your RMarkdown file and knitted HTML file

